%!TEX root = ../main.tex

\bigskip
\mhead{Relevant\\Experience}%
\textbf{“Grigore Moisil” Computer Science Regional Contest, Brasov, Romania} \newline
\emph{Several distinctions every year} \rdate{2012-2015}
\begin{itemize*}
  \item Attended every edition of the annual contest in multiple categories.
  \item Key skills developed: database development, product testing and presentation.
\end{itemize*}

\smallskip
\textbf{Continental Powertrain, Brasov, Romania} \newline
\emph{IT Department Intern} \rdate{2014}
\begin{itemize*}
  \item Had the opportunity to witness the inner workings of a modern factory from human
  resources to IT, from maintenance to production. Gained a deeper understanding of
  how different departments operate.
  \item Key skills developed: attention to detail.
\end{itemize*}

\smallskip
\textbf{National Physics Symposium, Brasov, Romania} \newline
\emph{Third place} \rdate{2013}
\begin{itemize*}
  \item Created and presented a cross-discipline project illustrating the usefulness of computer
  science in physics.
  \item Key skills developed: applying different concepts across disciplines, leading a team with
\end{itemize*}

\smallskip
\textbf{American Computer Science League, Pennsylvania, USA} \newline
\emph{Second Place in the Junior 5 Division} \rdate{2013}
\begin{itemize*}
  \item Gained a deeper understanding of a variety of subjects such as algorithmics,boolean
  algebra, digitalelectronics, graph theory and data structures.
  \item Key skills developed: teamwork, leadership, project planning.
\end{itemize*}
